DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox

### 2017-06-19 ase2017/paper.tex
improved Figure 1 of our tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
reviewed abstract of the tool paper
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}
We present an automated MATLAB Toolbox, named as DSSynth 
(Digital System Synthesis), to synthesize stable and safe digital-control 
systems for physical plants represented as linear time-invariant
systems with single-input and single-output. DSSynth synthesizes digital 
controllers w.r.t. the stability and safety specifications, considering finite word-length 
effects for physical plants represented by transfer-function or state-space 
equations. DSSynth considers fixed-point numerical representation for the 
digital controller and dynamic input ranges for the closed-loop control system. 
Currently, there are two DSSynth toolbox versions: command-line and 
MATLAB application. The resulting toolbox enables application of synthesis to 
real-world systems by control engineers.
\end{abstract}

@@

Control theory achieves the construction of reliable systems by 
offering mathematical guarantees about the stability and the desired 
performance of closed-loop systems, where plant states or outputs 
are fed back and compared to a reference signal to which a (designed) 
controller should maintain a set of control objectives~\cite{astrom1997computer}. 
Fig.~\ref{fig:typical-control-system} shows a typical closed-loop digital control system.

\textcolor{red}{Cristina, can you please draw this figure in tikz?}
\begin{figure}[ht!]
\centering
\includegraphics[width=0.35\textwidth]{closedloopseries.pdf}
\caption{Typical Closed-loop Control System.}
\label{fig:typical-control-system}
\end{figure}

>>>>

\begin{abstract}
We present an automated MATLAB Toolbox, named as DSSynth 
(Digital-System Synthesizer), to synthesize stable and safe digital controllers 
for physical plants represented as linear time-invariant
systems with single-input and single-output. In particular, DSSynth synthesizes digital 
controllers w.r.t. the stability and safety specifications by taking into account finite word-length 
effects. DSSynth considers the complete range
of approximations, including time discretization, quantization effects, 
and finite-precision arithmetic and its rounding errors. 
Currently, there are two DSSynth toolbox versions: command-line and 
MATLAB application for synthesizing digital controllers for physical plants 
represented by transfer-function or state-space equations. The resulting toolbox 
enables application of program synthesis to real-world systems by control engineers.
\end{abstract}

@@

Control theory achieves the construction of reliable systems by 
offering mathematical guarantees about the stability and the desired 
performance of closed-loop systems, where plant states or outputs 
are fed back and compared to a reference signal to which a (designed) 
controller should maintain a set of control objectives~\cite{astrom1997computer}. 
Fig.~\ref{fig:typical-control-system} shows a typical closed-loop digital control system.
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.35\textwidth]{closedloopseries.pdf}
\caption{Typical Closed-loop Control System.}
\label{fig:typical-control-system}
\end{figure}
